A Secondary Screen Architecture to Accurately Capture Viewers' Interactions in an iTV Environment

### 2014-08-22 src/paper.tex
Agradecimentos adicionados no paper
Modificação no final da conclusão para ajustar o comprimento do texto

\documentclass[conference,a4paper]{IEEEtran}

@@

\newcommand{\blurb}[1]{\marginpar{{\tt !!!}}{\tt [... #1 ...]}}
\renewcommand{\baselinestretch}{0.99}

@@

\author{\IEEEauthorblockN{Ricardo E. V. de S. Rosa}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\ Federal University of Minas Gerais \\ Av. Antônio Carlos 6627, 31270-901, \\Belo Horizonte, MG, Brazil\\
Email: ricardoerikson@ufmg.br}
\and
\IEEEauthorblockN{Lucas C. Cordeiro and Vicente F. de Lucena Junior}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\
Federal University of Amazonas \\
Manaus, AM, Brazil\\
Email: \{lucascordeiro,vicente\}@ufam.edu.br}
}
\maketitle

@@

A presence service detects physically nearby secondary screen devices that have the services necessary to establish a communication with an iTV device. Modern commercial operating systems for personal devices enable service discovery by using peer-to-peer or WiFi communication. This feature is particularly appropriated for the TV environment, once the secondary screen device must be wirelessly linked up with the iTV device. The devices are synchronized in order to update the contextual data about the viewer profile and the amount of people using a secondary device in the room. This contextual data can be used to learn how a viewer behaves towards other viewers.

@@

The architecture described in this paper is also technically feasible to implement in Digital TV (DTV) systems and can be particularly interesting for CPs in DTV standards, e.g., the Brazilian (ISDB-TB) and the Japanese(ISDB-T). These standards support the use of mobile devices as part of the system. Since the mobile devices support the implementation of the DTV middleware, a cooperative exhibition of the DTV application can be managed with the iTV device, thus enabling the capture of viewers' interactions and contextual data.

>>>>

\documentclass[conference,a4paper]{IEEEtran}
\IEEEoverridecommandlockouts

@@

\newcommand{\blurb}[1]{\marginpar{{\tt !!!}}{\tt [... #1 ...]}}
\renewcommand{\baselinestretch}{0.98}

@@

\author{\IEEEauthorblockN{Ricardo E. V. de S. Rosa}
\thanks{This research was supported by SAMSUNG, CAPES, FAPEAM, and CNPq grants.}\IEEEauthorblockA{Graduate Program in Electrical Engineering \\ Federal University of Minas Gerais \\ Av. Antônio Carlos 6627, 31270-901, \\Belo Horizonte, MG, Brazil\\
Email: ricardoerikson@ufmg.br}
\and
\IEEEauthorblockN{Lucas C. Cordeiro and Vicente F. de Lucena Junior}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\
Federal University of Amazonas \\
Manaus, AM, Brazil\\
Email: \{lucascordeiro,vicente\}@ufam.edu.br}
}

\maketitle

@@

A presence service detects physically nearby secondary screen devices that are able to establish a communication with an iTV device. Modern operating systems for personal devices enable service discovery by using peer-to-peer or WiFi communication. This feature is particularly appropriated for the TV environment, once the secondary screen device must be wirelessly linked up with the iTV device. The devices are synchronized in order to update the contextual data about the viewer profile and the amount of people using a secondary device in the room. This contextual data can be used to learn how a viewer behaves towards other viewers.

@@

The architecture described in this paper is also technically feasible to be implemented in Digital TV (DTV) systems and can be particularly interesting for content providers working with the Brazilian (ISDB-TB) or the Japanese(ISDB-T) DTV standard. These standards support the use of mobile devices as part of the system. Since the mobile devices support the implementation of the DTV middleware, a cooperative exhibition of the DTV application can be managed with the iTV device, thus enabling the capture of viewers' interactions and contextual data.
